---
title: "Run_Analytics Code Book"
author: "Joe DeMaro"
date: "September 5, 2018"
output: 
  html_document: default
---

## Purpose

#### The purpose of programming run_analytics.R is to learn how to create a tidy data set(tidydataset) from a large set of data.  The large data set was provided from study called 'Human Activity Recognition Using Smartphones Dataset'.  Each record in the original dataset included  
####1. Triaxial acceleration from the accelerometer (total acceleration) and the estimated body acceleration.
####2. Triaxial Angular velocity from the gyroscope. 
####3. A 561-feature vector with time and frequency domain variables. 
####4. Its activity label. 
####5. An identifier of the subject who carried out the experiment.

#### The larger set was processed by combining the test and training sets of data together maintaining subject and activity identity. Column names were added to describe the different data points collected per record.

#### Data was tidied by cleaning up column names, substituting activity names for identifiers and finally summarizing the data with mean or standard deviation as its metric.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Variable Description List

|Variable   |  Description|
|---------------| -------------|
|subject        |  ID integer used to signify an individual subject|  
|activity.str   |  Activity name (one of six activities.)   |
|domain| Time vs Frequency - designated by t or f in variable name|
|instrument| the device used to measure - a (accelerometer; acceleration) or g (gyroscope; velocity) in variable|
|calculated variable| mean or standard deviation|
|axis|XYZ direction|
|count|data points to calculate average|
|average|average by variable for each subject and activity|
|magnitude|magnitude of signal|
|jerk|jerk signal|


## Variable Summary

```{r echo=FALSE}
library(datasets)
data(tidydataset)
summary(tidydataset)
```

## Sample rows from Tidy data set
```{r}
head(tidydataset)
```

## Key variables
```{r}
#key(tidydataset)
```
## Data Structure of Tidy data set
```{r}
str(tidydataset)
```
## Tidy Dataset Variable Combinations
```{r}
colnames(tidydataset)
```

